Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach

### 2021-02-27 1_manuscript/itt-emotion_V6-5.tex
V6-5 -2191 words = 13,239 words

  In the last couple of decades, the economy of Japan has been affected by an increase in inbound international tourism \cite[][]{jones2009}. A year-on-year growth rate of 19.3\% was observed in 2017, with \num[group-separator={,}]{28691073} inbound tourists \cite[][]{jnto2003-2019}. The tourist population was 86.14\% Asian, and 25.63\% was from China. Western countries, including English-speaking countries in Europe, accounted for 11.4\% of the total, with 7.23\% being countries where English is the official or the de facto national language. The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon \cite[][]{sun2017}. The tourist market is gradually becoming diverse because of multicultural tourist populations. Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will be varied. Therefore, hotel management must cater to these expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.

>>>>

  Inbound international tourism has been increasingly affecting Japanese economy \cite[][]{jones2009}. A year-on-year growth rate of 19.3\% was observed in 2017, with \num[group-separator={,}]{28691073} inbound tourists \cite[][]{jnto2003-2019}. Chinese tourists accounted for 25.63\% of the tourist population. Western countries accounted for 11.4\% of the total, and 7.23\% were countries where English is the official or the de facto national language. The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon \cite[][]{sun2017}. Furthermore, the tourist market is gradually becoming diverse because of multicultural tourist populations. This diversity means that the expectations when staying at a hotel will be varied. Therefore, hotel management must cater to these expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
